%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Positions Held}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\emph{Post-Doctoral Fellow - Agence nationale de la recherche (ANR)} } % Job title
    {CNRS - Centre National de la Recherche Scientifique} % Organization
    {Lyon, France} % Location
    {2015 - Present} % Date(s)
    {
	  \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Engineered a high performance workflow for use on compute clusters that detects Pseudo-Autosomal boundaries in sex chromosomes using next generation sequencing data.}
		\item {Detecting and comparing Pseudo-Autosomal boundaries in sex chromosomes of Primates in the context of theoretical variation in sexual antagonism.}
		\item {Investigating the sex determination system of \textit{Ellobius} (Mole Vole) species with missing Y chromosomes using next generation sequencing data and recently assembled reference genomes.}
		\item {Co-authored a review of plant sex chromosome evolution, in particular contributing publication quality conceptual diagrams.}
	  \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {\emph{Research Assistant}} % Job title
    {Centre for Ecosystem Management} % Organization
    {Joondalup, Australia} % Location
    {2011 - 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisting with the study of Australian seed shrimp evolution and taxonomy using molecular and morphological techniques.}
        \item {Extraction of DNA from soil microbes to understand the role of soil heavy metal concentration/abundance in the development of bacterial antibiotic resistance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\emph{Research Assistant}} % Job title
    {MiWER (Mine Water and Environment Research Centre)} % Organization
    {Joondalup, Australia} % Location
    {2008 - 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Organisation of experiment monitoring and maintenance, around full time university study.}
        \item {Construction and maintenance of experiments, ground and surface water quality monitoring, profiling of pit lake water quality, zooplankton collection, phytoplankton collection, diatom collection, macroinvertebrate collection and identification.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\emph{Driller's Assistant}} % Job title
    {Wallis Drilling} % Organization
    {Murrin Murrin, Australia} % Location
    {2007} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {\emph{Supply officer \& Delivery Driver}} % Job title
    {Orbit Fitness} % Organization
    {Osborne Park, Australia} % Location
    {2001 - 2006} % Date(s)
    {
    }

%---------------------------------------------------------
\end{cventries}
